---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# expodiff

<!-- badges: start -->
<!-- badges: end -->

The goal of expodiff is to provide an interactive exploration of World Expos and Specialised Expos data, allowing users to visualize and compare key metrics like attending countries, area size, visitors, and economic factors. The package includes a Shiny app that enables dynamic data exploration and interactive visualizations.

## Installation

You can install the development version of expodiff from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-cherylbunny")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(expodiff)
# Launch the Shiny app
launch_expodiff()
```

The Shiny app provides various visualizations and comparisons, such as:

* Average attending countries over time for World and Specialised Expos.
* Correlation between area size and number of visitors.
* Top themes from Expos, ranked based on frequency.
* Economic factors and scale comparisons between different types of Expos.

## Data Summary

The data behind the expodiff package includes:

* World Expo and Specialised Expo data: covering attending countries, visitors, cost, area, and themes.

* Interactive visualizations: using plotly and ggplot2 to create responsive and dynamic charts.

* Economic analysis: a summary table comparing cost, visitors, and attending countries for World Expos and Specialised Expos.

## Example of Data Summary

You can summarize the built-in data sets:
```{r}
# Load the combined dataset
data("combined_data", package = "expodiff")

# Example summary of attending countries
summary(combined_data$summary_combined)
```


